---
title: "nbashotpackage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{nbashotpackage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(nbashotpackage)
library(dplyr)
library(ggplot2)
library(patchwork)
```

## Introduction

The **nbashotspackage** provides tools to explore a data set that contains NBA shooting data from the 2001-2002 and 2021-2022 seasons (2 seasons).

This vignette takes users through a basic demonstration that encapsulates the purpose of this package. It will explore:

1. Load the data set included `clean_data`.
2. Utilise the `analyse_shots()` function.
3. Output interpretation from this analysis
4. Launch the interactive Shiny app that is included in the package. 

The goal of this is to allow users to compare shot selection between the two seasons, specifically when it comes to the frequency of 2-pointer and 3-pointer shots. 

## The Data

